---
title: "Blogdown: build your homepage and create content"
subtitle: "R à Québec Workshop"
author: "Mamadou Yauck & Sergio Ewane Ebouele"
date: "2019-05-13"
output:
  xaringan::moon_reader:
    css: ["default-fonts","default","rladies-fonts", "rladies"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      includes:
      in_header: header.html
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(tidy = FALSE, eval = FALSE)
```


class: inverse, center, middle

# Explore your new site

---
#Hugo directory structure

```{r}
.
├── archetypes
├── config
├── config.toml
├── content
├── public
├── static
├── themes
```

---
#Hugo directory structure

```{r}
.
├── archetypes
{{├── config}}
├── config.toml
├── content
├── public
├── static
├── themes
```

---
#Hugo directory structure

```{r}
.
├── archetypes
├── config
{{├── config.toml}}
├── content
├── public
├── static
├── themes
```
---
#Hugo directory structure

```{r}
.
├── archetypes
├── config
├── config.toml
{{├── content}}
    └── author
    └── home
    └── post
├── public
├── static
├── themes
```

---
#Hugo directory structure

```{r}
.
├── archetypes
├── config
├── config.toml
├── content
├── public
{{├── static}}
    └── img
├── themes
```

---

#Serve your site (locally)

--

- Console

```{r}
blogdown::serve_site()
```

--

- [The RStudio Addin `Serve Site`](https://rstudio.github.io/rstudioaddins/)

---
class: inverse, center, middle

#Edit your new site

For more details, see [Academic's page builder](https://sourcethemes.com/academic/docs/page-builder/)

---
class: inverse, center, middle

#Edit your new site
##Edit your home page

---
##Change your bio

```{r}
.
├── archetypes
├── config
├── config.toml
{{├── content}}
    └── author
      └── admin
        └── index.md
├── public
├── static
├── themes
```


---
##Update your CV

```{r}
.
├── archetypes
├── config
├── config.toml
{{├── content}}
    └── home
      └── accomplishments.md
      └── experience.md
      └── skills.md
      └── ...
├── public
├── static
├── themes
```

---
#Edit the navigation bar


```{r}
.
├── archetypes
{{├── config}}
    └── .default
      └── menus.toml
├── config.toml
├── content
├── public
├── static
├── themes
```

---
class: inverse, center, middle

#Create a new post

---
#New post

--
- Console

```{r}
blogdown::new_post()
```
--
- From the `R` menu: `Addins -> New Post`


---
class: inverse, center, middle

#Feel free to edit your site !

